An Overview of Distributed Version Control Systems

### 2010-07-03 laarsample.tex
Sawtooth está bien :)
Ajustada la sección Small, Coherent and Logica commits

\subsection{Small, Coherent and Logical Commits}
%
% Dar vuelta la redacción. Tree son changesets => 
%
Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic, making the merging process easier by selecting only those commits that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking''. It has the advantage of using the revision tree as a series of \emph{changesets} or \emph{patches} instead of just a series of static versions.

@@

% Reveer saw tooth a ver si se dice así de posta
Doing the math you will see that the resulting checkout is about 15MBs. SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB. You might notice that Git has a "saw tooth" shape. That's because Git regulary optimizes its repository.

>>>>

\subsection{Small, Coherent and Logical Commits}
A revision tree is composed of a series of \emph{changesets} or \emph{patches} instead of just a series of static versions. A changeset or patch
can be as little as a very specific piece of code inside a much bigger and already modified file. Selecting only portions of the whole modifications
allows the user to make smaller commits which can describe change sepparatedly. It would then be easier to make a merge since you can select
only a commit that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking''.

@@

Doing the math you will see that the resulting checkout is about 15MBs. SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB. You might notice that Git has a sawtooth shape. That's because Git regulary optimizes its repository.
